Jilbert's Distinction Centrality

### 2025-07-05 index.qmd
updated function
fixed function
new func who dis

```{r Loading Functions}
   library(igraph)
   library(ggraph)
   library(here)
   library(networkdata)
   library(ggpubr)
   library(here)
   source("distinction.R")
```

@@

@@

>>>>

```{r Loading Functions}
   library(igraph)
   library(ggraph)
   library(here)
   library(networkdata)
   library(ggpubr)
   source("distinction.R")
```

@@

```{r}
   source("distinction.new.R")
   distinction.new(g1, norm = TRUE)
   distinction.new(g1, norm = FALSE)
```

@@

```{r}
   source("distinction.R")
   g <- as.matrix(read.csv(here("Data", "searchmodeltest.csv")))
   g <- graph_from_edgelist(g, directed = FALSE)
   distinction(g)
```
